\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{url}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{lmodern, amsfonts,amsmath,amstext,amsbsy,amssymb,amsopn,amsthm,upref,eucal,mathptmx,mathtools,url}

%NEW COMMAND
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
  
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command


%--------------------TITLE-------------
\par{\centering
		{\Huge Davide \textsc{Ravotti}
	}\bigskip\par}

%--------------------SECTIONS-----------------------------------


%Section: Personal Data
\section{Personal Data}

\begin{tabular}{rl}
    \textsc{Place and Date of Birth:} & Savigliano (CN), Italy | 02 August 1989 \\
    \textsc{Address:}  & School of Mathematical Sciences, Monash University \\
 & 9 Rainforest Walk, Clayton Campus, Victoria 3800 Australia \\
    \textsc{Nationality:}  & Italian \\
    \textsc{email:}  & \href{mailto:davide.ravotti@gmail.com}{davide.ravotti@gmail.com} \\
& \href{mailto:davide.ravotti@monash.edu}{davide.ravotti@monash.edu} \\
    \textsc{Website:} & \href{https://davideravotti.github.io/}{\url{https://davideravotti.github.io/}}
\end{tabular}

%%%%%

%Section: Education
\section{Education}
\begin{longtable}{r|p{11cm}}
 \textsc{2018} & Ph.D.~degree at the University of Bristol (Bristol, UK). \\
& Supervisor: prof.~Corinna Ulcigrai. \\ 
& Thesis title: \emph{Mixing via shearing in some parabolic flows}. \\
%
\multicolumn{2}{c}{} \\
%
\textsc{2014} & Diploma di Licenza of the Scuola Superiore of the University of Udine (Udine, Italy). \\ 
& Final mark: 110/110 \emph{cum laude}. \\
%
\multicolumn{2}{c}{} \\
%
\textsc{2013} & Master degree in Mathematics, University of Udine (Udine, Italy). \\
& Thesis advisor: prof.~Giovanni Panti. \\
& Thesis title: \emph{Misiurewicz parameters for the quadratic family} (in Italian). \\
& Final mark: 110/110 \emph{cum laude}. \\
%
\multicolumn{2}{c}{} \\
%
\textsc{2011} & Bachelor degree in Mathematics, University of Udine (Udine, Italy). \\
& Thesis advisor: prof.~Giovanni Panti. \\
& Thesis title: \emph{Generalized Farey enumerations} (in Italian). \\
& Final mark: 110/110 \emph{cum laude}. \\
%
\multicolumn{2}{c}{} \\
%
\textsc{2008} & Scientific high school degree at Liceo Scientifico \lq\lq G. Ancina\rq\rq\ (Fossano, Italy).\\
& Final mark: 100/100.
\end{longtable}

%%%%%

%Section: Academic positions
\section{Academic Positions}
\begin{longtable}{rl}	
 \textsc{Mar.~2019-present} & Research Fellow, Monash University (Melbourne, Australia). \\
%
\textsc{Sep.~2018-Mar.~2019} & Postdoctoral Assistant, University of Z\"{u}rich (Z\"{u}rich, Switzerland). \\ 
%
\textsc{Apr.~2018-Aug.~2018} & Research Associate, University of Bristol (Bristol, UK).
\end{longtable}

%%%%%

%Section: Seminars
\section{Seminars}
\begin{longtable}{rl}	
%\textsc{?? Jul.~2019} & Conference \lq\lq Dynamics of Parabolic Flows\rq\rq\ (Z\"{u}rich, Switzerland). \\
%
\textsc{27 Mar.~2019} & Monash University (Melbourne, Australia). \\
%
\textsc{05 Dec.~2018} & Scuola Normale Superiore (Pisa, Italy). \\ 
%
\textsc{03 Sep.~2018} & Conference \lq\lq Dynamics Days Europe\rq\rq\ (Loughborough, UK). \\
%
\textsc{16 Jan.~2018} & Queen Mary University (London, UK). \\
%
\textsc{02 Nov.~2017} & Scuola Normale Superiore (Pisa, Italy).\\
%
\textsc{17 Oct.~2017} & University of Warwick (Coventry, UK). \\
%
\textsc{12 Oct.~2017} & University of Manchester (Manchester, UK). \\
%
\textsc{24 Aug.~2017} & Conference \lq\lq Dynamics in Number Theory and Geometry\rq\rq\ (Kingston, \\
& Canada). \\
%
\textsc{06 Jun.~2017} & Workshop \lq\lq Modern Trends in the Ergodic Theory of Dynamical Systems\rq\rq\\
&(Rome, Italy). \\
%
\textsc{23 Mar.~2017} & University of Bristol (Bristol, UK). \\
%
\textsc{11 Jan.~2017} & One-day Workshop on Dynamical Systems, ICTP (Trieste, Italy). \\
%
\textsc{10 Jan.~2017} & University of Udine (Udine, Italy). \\
\end{longtable}

%%%%%

%Section: Schools and Conferences
\section{Participation in Schools and Conferences}
\begin{tabularx}{\linewidth}{r X}
%\textsc{01-05 Jul.~2019} & Conference \lq\lq Dynamics of Parabolic Flows\rq\rq\ (Z\"{u}rich, Switzerland). \\
%
\textsc{03-07 Sep.~2018} & Conference \lq\lq Dynamics Days Europe\rq\rq\ (Loughborough, UK). \\
%
\textsc{10-16 Jun.~2018} & Conference \lq\lq Ergodic aspects of modern dynamics\rq\rq\ (Bedlewo, Poland). \\ 
%
\textsc{19-23 Mar.~2018} & Symposium \lq\lq Teichm\"{u}ller Dynamics\rq\rq\ (Warwick, UK). \\
%
\textsc{21-25 Aug.~2017} & Conference \lq\lq Dynamics in Number Theory and Geometry\rq\rq\ (Kingston, Canada). \\
%
\textsc{05-09 Jun.~2017} & Workshop \lq\lq Modern Trends in the Ergodic Theory of Dynamical Systems\rq\rq\ (Rome, Italy).\\
%
\textsc{01-04 Aug.~2016} & Conference \lq\lq Young Researchers in Mathematics\rq\rq\ (St.~Andrews, UK). \\
%
\textsc{27 Jun.-2 Jul.~2016} & Workshop \lq\lq Analytical Methods in Classical and Quantum Dynamical Systems\rq\rq\ (Pisa, Italy). \\
%
\textsc{21-24 Mar.~2016} & Conference \lq\lq BMC\rq\rq\ (Bristol, UK). \\
%
\textsc{22-28 Nov.~2015} & Simons semester workshop \lq\lq Ergodic Theory of Dynamical Systems\rq\rq\ (Bedlewo, Poland). \\
%
\textsc{29 Jun.-3 Jul.~2015} & Workshop \lq\lq Group representations in Dynamics and Geometry\rq\rq\ (Luminy, France). \\
%
\textsc{22-25 Jun.~2015} & Workshop \lq\lq DinAmicI – Italian people in Dynamics\rq\rq\ (Corinaldo, Italy). \\
%
\textsc{13-17 Apr.~2015} & LMS-CMI Research School \lq\lq Statistical Properties of Dynamical Systems\rq\rq\ (Loughborough, UK). \\
%
\textsc{4-14 Jun.~2014} & ICTP-NLAGA School \lq\lq Dynamical Systems and Ergodic Theory\rq\rq\ (Mbour, Senegal). \\
\end{tabularx}

%%%%%

%Section: Teaching
\section{Teaching and Other Activities}
\begin{tabularx}{\linewidth}{r X}
%\textsc{??} & Tutor \\
%
\textsc{Jul.~2018} & Tutor at the \emph{ICTP Summer School in Dynamics}. \\
%
\textsc{2017/18} & Tutor for the first year courses \emph{Analysis 1} and \emph{Foundations and Proof}.\\
& Organiser of the Reading group in \emph{Representation Theory of Semisimple Lie Groups}.\\
%
\textsc{2016/17} & Tutor for the first year courses \emph{Analysis 1} and \emph{Foundations and Proof}.\\
& Tutor for the second year course \emph{Introduction to Geometry}.\\
& Organiser of the \emph{Pure postgraduates seminars}.\\
& Organiser of the \emph{ChaParDyn Reading group}.\\
%
\textsc{2015/16} & Tutor for the first year courses \emph{Analysis 1} and \emph{Linear Algebra and Geometry}.\\
& Organiser of the \emph{Pure postgraduates seminars}.\\
& Organiser of the Reading group in \emph{Teichm\"{u}ller Theory}.\\
%
\textsc{2014/15} & Marker for the courses \emph{Ergodic Theory and Dynamical Systems} and \emph{Algebra II}.\\
\end{tabularx}

%%%%%

\vspace{10pt}
%Section: Service
\section{Service to the Community}
Referee for: %Inventiones Mathematicae,
Discrete and Continuous Dynamical Systems. 

%%%%%

\vspace{10pt}
%Section: Language
\section{Language Skills}
\textsc{Italian} (native language).\\
\textsc{English} (fluent).\\
\textsc{French} (intermediate).\\
\textsc{Japanese} (basic).

%%%%%

%Section: Publications
\section{Publications and Preprints}
\begin{tabularx}{\linewidth}{r X}
[1] & A.~Avila, G.~Forni, D.~Ravotti, C.~Ulcigrai. Mixing for smooth time-changes of general nilflows. \emph{Preprint arXiv:1905.11628}, 2019.\\
%
$[2]$ & D.~Ravotti. Parabolic perturbations of unipotent flows on compact quotients of SL$(3, \mathbb{R})$. 
Accepted for publication in \emph{Comm.~Math.~Phys.} \\
%
$[3]$ & D.~Ravotti. Mixing for suspension flows over skew-translations and time-changes of quasi-abelian filiform nilflows. Accepted for publication in \emph{Ergod.~Theory Dyn.~Syst.}\\
%
$[4]$ & D.~Ravotti. Quantitative mixing for locally Hamiltonian flows with saddle loops on compact surfaces. \emph{Ann.~Henri Poincaré}, 18(12):3815--3861, 2017.\\
%
$[5]$ & G.~Panti, D.~Ravotti. Measures induced by units. \emph{J.~Symb.~Log.}, 78(3):886--910, 2013.\\
\end{tabularx}

\vspace{20pt}

30 May 2019.




\end{document}

















\section{Interests and Activities}
Technology, Open-Source, Programming\\
Paradoxes in Decision Making, Psychoanalysis, Behavioural Finance\\
Football, Travelling

\newpage
\par{\centering\Large \hypertarget{grds}{Master of Science in \textsc{Finance}}\par}\large{\centering Grades\par}\normalsize
\begin{center}
\begin{tabular}{lcc}
\multicolumn{1}{c}{\textsc{Exam}}&\textsc{Grade}&\textsc{Credit Hrs}\\ \hline
Corporate Finance (Valuation)	&25&	6\\
Financial Statement Analysis	&28&	6\\
Statistics	&27&	6\\
Theory of Finance	&26&	6\\
Quantitative Methods for Finance	&30&	6\\
Econometrics	&24	&6\\
Derivatives	&31&	6\\
Management of Financial and Insurance Companies	&30&	6\\
Business Law	&31&	6\\
Investment Banking	&28&	6\\ \\
		
Behavioral Models for Economics and Finance	&29&	6\\
Numerical Methods for Finance	&29&	6\\
Advanced Derivatives	&30&	6\\
Fixed Income (Advanced Methods)	&30&	6\\ \\
		
English Language	&30&	4\\
French Language	&31&	4\\
		
Internship	&	&8\\
		
Final Thesis	&	&20\\
		
		& Total&120\\\cline{2-3}
&\textsc{Gpa}&\textbf{28.61}
\end{tabular}
\end{center}
\bigskip
\hrule
\bigskip
\par{\centering\Large \hypertarget{grds_cleli}{Undergraduate Degree in \textsc{Law and Business Administration}}\par}\large{\centering Grades\par}\normalsize

\begin{center}

\tablefirsthead{%
  \multicolumn{1}{c}{\textsc{Esame (\textsc{ita})}}&\multicolumn{1}{c}{\textsc{Exam (\textsc{eng})}}&\textsc{Grade}&\textsc{Credit Hrs}\\ \hline}
\tablehead{%
\multicolumn{1}{c}{\textsc{Esame (\textsc{ita})}}&\multicolumn{1}{c}{\textsc{Exam (\textsc{eng})}}&\textsc{Grade}&\textsc{Credit Hrs}\\ \hline
}
\tabletail{%
}
\tablelasttail{}	

 \begin{supertabular}{p{4.9cm} p{4.9cm} c c}
Economia aziendale&Theory and principles of management& 28 & 8\\
Istituzioni di diritto privato&Principles of private law&30&8\\
 Istituzioni di diritto pubblico 
&
 Principles of public law 
& 30&
 6 
\\
Matematica generale 
& Mathematics 
&31&8\\
 Contabilit\`a e Bilancio 
& Accounting and Financial statements 
& 31 & 8\\
 Diritto del lavoro 
&
 Labour law 
& 30&
4 
\\
 Informatica & Computer skills &29& 4 
\\
 Economia e gestione delle imprese & Corporate management &31&6 
\\
 Microeconomia & Microeconomics &30&8 
\\
 Contabilit\`a e bilancio 2 & Accounting and financial statements 2 
&29&8 \\
 Diritto commerciale & Company and business law &30&8 
\\
 Macroeconomia & Macroeconomics &29&8 
\\
 Statistica & Statistics &30&6\\
 Diritto delle procedure concorsuali & Insolvency law &31&4 
\\
 Finanza aziendale 
& Corporate finance 
&31 &8 \\
 Matematica finanziaria & Financial mathematics &31&4 
\\
 Programmazione e controllo 
& Management accounting &31&8 
\\
Lingua Inglese \textsc{c1}& English Language \textsc{c1}& 25&6\\ 
Diritto tributario & Tax law &30&6 
\\
Organizzazione e sistemi informativi aziendali &Management information systems &28&6 
\\
 Strategia e politica aziendale* 
& Business strategy* & 29& 6 
\\
Derivati*&Derivatives*&30&6\\
Opzionale all'estero* & Corporate Financial Strategy* &30&6\\
Lingua Francese \textsc{b1} & French Language \textsc{b1}&31&6\\
Economia dei mercati e degli intermediari finanziari* 
&Financial markets and institutions* &30&6 
\\
Revisione aziendale 
&Financial auditing &31&6 
\\
Scienza delle finanze &Public economics &30&6 
\\
 Lavoro finale& Final report&&6\\
& & Total&180\\\cline{3-4}
& &\textsc{Gpa}&\textbf{29.85}\\ \\ \multicolumn{4}{l}{\footnotesize A star (*) indicates that the course was taken at the \textbf{University of Southern California}, Los Angeles, \textsc{usa}}
 \end{supertabular}
\end{center}
\bigskip
\hrule
\bigskip
\par{\centering\Large \hypertarget{grds_usc}{Exchange Program at \textsc{usc}, Los Angeles}\par}\large{\centering Grades\par}\normalsize

\begin{center}
\begin{tabular}{lcc}
\multicolumn{1}{c}{\textsc{Exam}}&\textsc{Grade}&\textsc{Grade Points}\\ \hline
Corporate Financial Strategy	&A&	4\\
Derivatives	&A&	4\\
Money, Credit, and Banking	&A&	4\\
Business Strategy & A-& 3.5\\
& &\\\cline{2-3}
 &\textsc{Gpa}&\textbf{3.875}
\end{tabular}
\end{center}
%\newpage
%\hypertarget{gmat}{\textsc{Gmat}\setmainfont{LMRoman10 Regular}\textregistered\setmainfont[SmallCapsFont=Fontin-SmallCaps]{Fontin-Regular}}

%\XeTeXpdffile ''GMAT.pdf'' page 1 scaled 800

\end{document}